---
title: "Expedition eDNA Plots and Stats Analysis"
output: html_notebook
---
 

<br/>
<br/>

 

# Load packages

```{r}
# rm(list = ls())
library(tidyverse)
library(phyloseq)
library(vegan)
library(RColorBrewer)
library(microbiome)
library(metagMisc)
library(fantaxtic)
library(ggrepel)
library(paletteer)
library(pals)
library(compositions)
library(hms)
# library(ggvegan)
```

#  Import and prepare data

Import-

## 2024 Expedition samples**
### Mifish-
```{r}
asv_count_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh-expedition/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count_mifish) <- asv_count_mifish$x
asv_count_mifish <- asv_count_mifish %>% select(-x)
asv_count_mifish_mat <- as.matrix(asv_count_mifish)

asv_taxonomy_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh-expedition/ASV2Taxonomy/results-revamp-2024-MiFish-expedition_asvTaxonomyTable_NOUNKNOWNS.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy_mifish) <- asv_taxonomy_mifish$ASV
asv_taxonomy_mifish <- asv_taxonomy_mifish %>% select(-ASV)
asv_taxonomy_mifish_mat <- as.matrix(asv_taxonomy_mifish)



sample_metadata_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh-expedition/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)

# also import and join CTD values averaged over each eDNA sampling interval
sample_metadata2 <- read.csv("/Volumes/easystore/eDNA/shirp-edna/figures-expedition/CTD_avg_eDNA_sample_intervals.csv")

sample_metadata_mifish <- left_join(sample_metadata_mifish, sample_metadata2, by = c("Name.Deploy_Cartr_Library" = "Deploy_Cartr_Library"))

row.names(sample_metadata_mifish) <- sample_metadata_mifish$Sample
sample_metadata_mifish <- sample_metadata_mifish %>% select(-Sample)

ASV_2024_exp_mifish = otu_table(asv_count_mifish_mat, taxa_are_rows = TRUE)
TAX_2024_exp_mifish = tax_table(asv_taxonomy_mifish_mat)
samples_2024_exp_mifish = sample_data(sample_metadata_mifish)

phylo_2024_exp_mifish <- phyloseq(ASV_2024_exp_mifish, TAX_2024_exp_mifish, samples_2024_exp_mifish)


```

### Elas02-
```{r}
asv_count_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02-expedition/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count_elas) <- asv_count_elas$x
asv_count_elas <- asv_count_elas %>% select(-x)
asv_count_elas_mat <- as.matrix(asv_count_elas)

asv_taxonomy_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02-expedition/ASV2Taxonomy/results-revamp-2024-Elas02-expedition_asvTaxonomyTable_NOUNKNOWNS.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy_elas) <- asv_taxonomy_elas$ASV
asv_taxonomy_elas <- asv_taxonomy_elas %>% select(-ASV)
asv_taxonomy_elas_mat <- as.matrix(asv_taxonomy_elas)

sample_metadata_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02-expedition/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)

sample_metadata_elas <- left_join(sample_metadata_elas, sample_metadata2, by = c("Name.Deploy_Cartr" = "Name.Deploy_Cartr"))

row.names(sample_metadata_elas) <- sample_metadata_elas$Sample
sample_metadata_elas <- sample_metadata_elas %>% select(-Sample)

ASV_2024_exp_elas = otu_table(asv_count_elas_mat, taxa_are_rows = TRUE)
TAX_2024_exp_elas = tax_table(asv_taxonomy_elas_mat)
samples_2024_exp_elas = sample_data(sample_metadata_elas)

phylo_2024_exp_elas <- phyloseq(ASV_2024_exp_elas, TAX_2024_exp_elas, samples_2024_exp_elas)


```


### CO1-

```{r}
asv_count <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1-expedition/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)

row.names(asv_count) <- asv_count$x
asv_count <- asv_count %>% select(-x)
asv_count_mat <- as.matrix(asv_count)

asv_taxonomy <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1-expedition/results-revamp-2024-CO1-expeditiona_asvTaxonomyTable_fixed.txt", header=TRUE, stringsAsFactors=FALSE)

asv_taxonomy <- full_join(asv_taxonomya, asv_taxonomyb) %>% full_join(asv_taxonomyc)

row.names(asv_taxonomy) <- asv_taxonomy$ASV
asv_taxonomy <- asv_taxonomy %>% select(-ASV)
asv_taxonomy_mat <- as.matrix(asv_taxonomy)

sample_metadata <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1-expedition/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)
sample_metadata$Deployment <- as.factor(sample_metadata$Deployment)
sample_metadata$sites <- as.factor(sample_metadata$sites)

row.names(sample_metadata_co1) <- sample_metadata_co1$Sample
sample_metadata_co1 <- sample_metadata_co1 %>% select(-Sample)


ASV_2024_exp_co1 = otu_table(asv_count_mat, taxa_are_rows = TRUE)
TAX_2024_exp_co1 = tax_table(asv_taxonomy_mat)
samples_2024_exp_co1 = sample_data(sample_metadata_co1)


# set NAs to zeroes
ASV_2024_exp_co1[is.na(ASV_2024_exp_co1)] <- 0


phylo_2024_exp_co1 <- phyloseq(ASV_2024_exp_co1, TAX_2024_exp_co1, samples_2024_exp_co1)

```






## 2024 Manual samples**
To compare September hand samples directly to USV-RoCSI samples
### Mifish-
```{r}
asv_count_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count_mifish) <- asv_count_mifish$x
asv_count_mifish <- asv_count_mifish %>% select(-x)
asv_count_mifish_mat <- as.matrix(asv_count_mifish)

asv_taxonomy_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh/ASV2Taxonomy/results-revamp-2024-MiFish_asvTaxonomyTable_NOUNKNOWNS.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy_mifish) <- asv_taxonomy_mifish$ASV
asv_taxonomy_mifish <- asv_taxonomy_mifish %>% select(-ASV)
asv_taxonomy_mifish_mat <- as.matrix(asv_taxonomy_mifish)

sample_metadata_mifish <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-MiFIsh/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)
row.names(sample_metadata_mifish) <- sample_metadata_mifish$Sample
sample_metadata_mifish <- sample_metadata_mifish %>% select(-Sample)

ASV_2024_trawl_mifish = otu_table(asv_count_mifish_mat, taxa_are_rows = TRUE)
TAX_2024_trawl_mifish = tax_table(asv_taxonomy_mifish_mat)
samples_2024_trawl_mifish = sample_data(sample_metadata_mifish)

phylo_2024_trawl_mifish <- phyloseq(ASV_2024_trawl_mifish, TAX_2024_trawl_mifish, samples_2024_trawl_mifish)


```

### Elas02-
```{r}
asv_count_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count_elas) <- asv_count_elas$x
asv_count_elas <- asv_count_elas %>% select(-x)
asv_count_elas_mat <- as.matrix(asv_count_elas)

asv_taxonomy_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02/ASV2Taxonomy/results-revamp-2024-Elas02_asvTaxonomyTable_NOUNKNOWNS.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy_elas) <- asv_taxonomy_elas$ASV
asv_taxonomy_elas <- asv_taxonomy_elas %>% select(-ASV)
asv_taxonomy_elas_mat <- as.matrix(asv_taxonomy_elas)

sample_metadata_elas <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-Elas02/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)
row.names(sample_metadata_elas) <- sample_metadata_elas$Sample
sample_metadata_elas <- sample_metadata_elas %>% select(-Sample)

ASV_2024_trawl_elas = otu_table(asv_count_elas_mat, taxa_are_rows = TRUE)
TAX_2024_trawl_elas = tax_table(asv_taxonomy_elas_mat)
samples_2024_trawl_elas = sample_data(sample_metadata_elas)

phylo_2024_trawl_elas <- phyloseq(ASV_2024_trawl_elas, TAX_2024_trawl_elas, samples_2024_trawl_elas)


```

### CO1
```{r}
asv_counta <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1/ASV2Taxonomy/ASVs_counts_NOUNKNOWNS.tsv", header=TRUE, stringsAsFactors=FALSE)

row.names(asv_count) <- asv_count$x
asv_count <- asv_count %>% select(-x)
asv_count_mat <- as.matrix(asv_count)

asv_taxonomy <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1T/results-revamp-2024-CO1_Updated_asvTaxonomyTable_fixed.txt", header=TRUE, stringsAsFactors=FALSE)

row.names(asv_taxonomy) <- asv_taxonomy$ASV
asv_taxonomy <- asv_taxonomy %>% select(-ASV)
asv_taxonomy_mat <- as.matrix(asv_taxonomy)

sample_metadata <- read.delim("/Volumes/easystore/eDNA/shirp-edna/results-revamp-2024-CO1/sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)

row.names(sample_metadata_co1) <- sample_metadata_co1$Sample
sample_metadata_co1 <- sample_metadata_co1 %>% select(-Sample)

ASV_2024_trawl_co1 = otu_table(asv_count_mat, taxa_are_rows = TRUE)
TAX_2024_trawl_co1 = tax_table(asv_taxonomy_mat)
samples_2024_trawl_co1 = sample_data(sample_metadata_co1)


# set NAs to zeroes
ASV_2024_trawl_co1[is.na(ASV_2024_trawl_co1)] <- 0


phylo_2024_trawl_co1 <- phyloseq(ASV_2024_trawl_co1, TAX_2024_trawl_co1, samples_2024_trawl_co1)

```






For this analysis, I am only using the trawl results that coincide with the expedition (will do the rest of the season in another analysis).

Filter by date (expedition was 9/10-9/19/24)

```{r}
phylo_2024_trawl_mifish = subset_samples(phylo_2024_trawl_mifish, Datecode %in% c("20240910","20240916"))

phylo_2024_trawl_elas = subset_samples(phylo_2024_trawl_elas, Datecode %in% c("20240910","20240916"))

phylo_2024_trawl_co1 = subset_samples(phylo_2024_trawl_co1, Datecode %in% c("20240910","20240916"))
```

#### Save variables up to here 
```{r}
save.image(file = "figures-expedition/phyloseq_objects_unfiltered.RData")
```

load if returning
```{r}
load("figures-expedition/phyloseq_objects_unfiltered.RData")
```







# QC and filtering

View sample sums, sort from min to max, to flag low-sequencing-effort samples:
```{r}
as.data.frame(sort(sample_sums(phylo_2024_exp_mifish)))
as.data.frame(sort(sample_sums(phylo_2024_exp_elas)))
as.data.frame(sort(sample_sums(phylo_2024_exp_co1)))

as.data.frame(sort(sample_sums(phylo_2024_trawl_mifish)))
as.data.frame(sort(sample_sums(phylo_2024_trawl_elas)))
as.data.frame(sort(sample_sums(phylo_2024_trawl_co1)))


```




## Curating

### Replace NAs in taxonomy 

Check what they look like before replacement
```{r}
# Exp/ MiFish
data.frame(tax_table(phylo_2024_exp_mifish)) # all taxa
data.frame(tax_table(subset_taxa(phylo_2024_exp_mifish, is.na(Species)))) # taxa with NAs

# Exp/ Elas
data.frame(tax_table(phylo_2024_exp_elas))
data.frame(tax_table(subset_taxa(phylo_2024_exp_elas, is.na(Species))))

# Exp/ CO1
data.frame(tax_table(phylo_2024_exp_co1))
data.frame(tax_table(subset_taxa(phylo_2024_exp_co1, is.na(Species))))


# Trawl/ MiFish
data.frame(tax_table(phylo_2024_trawl_mifish))
data.frame(tax_table(subset_taxa(phylo_2024_trawl_mifish, is.na(Species))))

# Trawl/ Elas
data.frame(tax_table(phylo_2024_trawl_elas))
data.frame(tax_table(subset_taxa(phylo_2024_trawl_elas, is.na(Species))))

# Trawl/ CO1
data.frame(tax_table(phylo_2024_trawl_co1))
data.frame(tax_table(subset_taxa(phylo_2024_trawl_co1, is.na(Species))))
```


```{r}
# Replace NA in taxa list with next highest annotated taxon
tax_table(phylo_2024_exp_mifish) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_exp_mifish, include_rank = T))

tax_table(phylo_2024_exp_elas) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_exp_elas, include_rank = T))

tax_table(phylo_2024_exp_co1) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_exp_co1, include_rank = T))

tax_table(phylo_2024_trawl_mifish) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_trawl_mifish, include_rank = T))

tax_table(phylo_2024_trawl_elas) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_trawl_elas, include_rank = T))

tax_table(phylo_2024_trawl_co1) <- tax_table(fantaxtic::name_na_taxa(phylo_2024_trawl_co1, include_rank = T))


# Check after replacement
data.frame(tax_table(phylo_2024_exp_mifish))
data.frame(tax_table(phylo_2024_exp_elas))
data.frame(tax_table(phylo_2024_exp_co1))

data.frame(tax_table(phylo_2024_trawl_mifish))
data.frame(tax_table(phylo_2024_trawl_elas))
data.frame(tax_table(phylo_2024_trawl_co1))

```




#### Start filtering by taxonomy

Meanwhile, rename *filtered* phyloseq objects to `ps` from `phylo`. 
So `ps2024_exp_mifish`. Unfiltered is `phylo_2024_exp_mifish`, etc.

##### Remove prokaryotes
MiFish/ Expedition-
```{r}
nrow(tax_table(phylo_2024_exp_mifish)) # number of taxa before filtering
ps2024_exp_mifish <- subset_taxa(phylo_2024_exp_mifish, !Kingdom == 'Bacteria')
nrow(tax_table(ps2024_exp_mifish)) # number of taxa left
unique(tax_table(ps2024_exp_mifish)[, 1])
```


Elas02/ Expedition-
There are no Bacteria in Exp/Elas02 library



CO1/ Expedition-
```{r}
nrow(tax_table(phylo_2024_exp_co1)) # number of taxa before filtering
ps2024_exp_co1 <- subset_taxa(phylo_2024_exp_co1, !Kingdom == 'Bacteria')
nrow(tax_table(ps2024_exp_co1)) # number of taxa left
unique(tax_table(ps2024_exp_co1)[, 1])
```


MiFish/ Trawl-
```{r}
nrow(tax_table(phylo_2024_trawl_mifish)) # number of taxa before filtering
ps2024_trawl_mifish <- subset_taxa(phylo_2024_trawl_mifish, !Kingdom == 'Bacteria')
nrow(tax_table(ps2024_trawl_mifish)) # number of taxa left
unique(tax_table(ps2024_trawl_mifish)[, 1])
```


Elas02/ Trawl-
There are no Bacteria in Exp/Elas02 library


CO1/ Trawl-
```{r}
nrow(tax_table(phylo_2024_trawl_co1)) # number of taxa before filtering
ps2024_trawl_co1 <- subset_taxa(phylo_2024_trawl_co1, !Kingdom == 'Bacteria')
nrow(tax_table(ps2024_trawl_co1)) # number of taxa left
unique(tax_table(ps2024_trawl_co1)[, 1])
```



##### Remove non-marine mammals

Exp/MiFish-
```{r}
as.data.frame(unique(tax_table(ps2024_exp_mifish)[, 7]))
nrow(tax_table(ps2024_exp_mifish)) # number of ASVs before filtering

ps2024_exp_mifish <- subset_taxa(ps2024_exp_mifish, !Species == 'Canis lupus' & !Species == 'Mus musculus' & !Species == 'Homo sapiens' & !Species == 'Sus scrofa' & !Species == 'Unknown Canis (Genus)' & !Species == 'Procyon lotor' & !Species == 'Bos taurus')

nrow(tax_table(ps2024_exp_mifish)) # number of ASVs left
as.data.frame(unique(tax_table(ps2024_exp_mifish)[, 7]))
```
1148 species taxa remain from the original 2085


Exp/Elas02- 
```{r}
nrow(tax_table(phylo_2024_exp_elas)) # number of taxa before filtering
ps2024_exp_elas <- subset_taxa(phylo_2024_exp_elas, !Class == 'Mammalia')
nrow(tax_table(ps2024_exp_elas)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_exp_elas)[, 7]))

```
1232 unique taxa remain



Exp/CO1- 
```{r}
nrow(tax_table(ps2024_exp_co1)) # number of taxa before filtering
ps2024_exp_co1 <- subset_taxa(ps2024_exp_co1, !Class == 'Mammalia')
nrow(tax_table(ps2024_exp_co1)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_exp_co1)[, 7]))

```
39,617 ASVs remain of the 39,640 eukaryotic ASVs


Trawl/MiFish-
```{r}
as.data.frame(unique(tax_table(ps2024_trawl_mifish)[, 7]))
nrow(tax_table(ps2024_trawl_mifish)) # number of ASVs before filtering

ps2024_trawl_mifish <- subset_taxa(ps2024_trawl_mifish, !Class == 'Mammalia')

nrow(tax_table(ps2024_trawl_mifish)) # number of ASVs left
as.data.frame(unique(tax_table(ps2024_trawl_mifish)[, 7]))
```
1417 unique taxa remain 


Trawl/Elas02- 
```{r}
nrow(tax_table(phylo_2024_trawl_elas)) # number of taxa before filtering
ps2024_trawl_elas <- subset_taxa(phylo_2024_trawl_elas, !Class == 'Mammalia')
nrow(tax_table(ps2024_trawl_elas)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_trawl_elas)[, 7]))

```
1528 unique taxa remain

Trawl/CO1
```{r}
nrow(tax_table(ps2024_trawl_co1)) # number of taxa before filtering
ps2024_trawl_co1 <- subset_taxa(ps2024_trawl_co1, !Class == 'Mammalia')
nrow(tax_table(ps2024_trawl_co1)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_trawl_co1)[, 7]))

```
34216 ASVs remain


##### Remove aves that are not waterfowl


```{r}
# subset_taxa(ps2024_exp_mifish, Class == 'Aves')

subset_taxa(ps2024_exp_elas, Class == 'Aves')
unique(tax_table(subset_taxa(ps2024_exp_elas, Class == 'Aves')))

subset_taxa(ps2024_trawl_mifish, Class == 'Aves')
unique(tax_table(subset_taxa(ps2024_trawl_mifish, Class == 'Aves')))

subset_taxa(ps2024_trawl_elas, Class == 'Aves')
unique(tax_table(subset_taxa(ps2024_trawl_elas, Class == 'Aves')))
```


```{r}
# ps2024_exp_mifish <-   subset_taxa(ps2024_exp_mifish, !Class == 'Aves')
nrow(tax_table(ps2024_exp_mifish)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_exp_mifish)[, 4]))
as.data.frame(unique(tax_table(ps2024_exp_mifish)[, 7]))

ps2024_exp_elas <-   subset_taxa(ps2024_exp_elas, !Class == 'Aves')
nrow(tax_table(ps2024_exp_elas)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_exp_elas)[, 4]))
as.data.frame(unique(tax_table(ps2024_exp_elas)[, 7]))

ps2024_trawl_mifish <-   subset_taxa(ps2024_trawl_mifish, !Class == 'Aves')
nrow(tax_table(ps2024_trawl_mifish)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_trawl_mifish)[, 4]))
as.data.frame(unique(tax_table(ps2024_trawl_mifish)[, 7]))

ps2024_trawl_elas <-   subset_taxa(ps2024_trawl_elas, !Class == 'Aves')
nrow(tax_table(ps2024_trawl_elas)) # number of taxa left
as.data.frame(unique(tax_table(ps2024_trawl_elas)[, 4]))
as.data.frame(unique(tax_table(ps2024_trawl_elas)[, 7]))
```






### Add in common names

Import common names from my ongoing list
```{r}
commonnames <- read_csv(file = "../eDNA-databases/commonnames.csv")
```

Update phyloseq objects with common name column
```{r}
# Extract, update, tax_table
taxonomy_exp_mifish <- as.data.frame(tax_table(ps2024_exp_mifish)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_exp_mifish) <- taxonomy_exp_mifish$ASV
taxonomy_exp_mifish <- taxonomy_exp_mifish %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_exp_mifish) <- as.matrix(taxonomy_exp_mifish)

taxonomy_exp_elas <- as.data.frame(tax_table(ps2024_exp_elas)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_exp_elas) <- taxonomy_exp_elas$ASV
taxonomy_exp_elas <- taxonomy_exp_elas %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_exp_elas) <- as.matrix(taxonomy_exp_elas)

taxonomy_exp_co1 <- as.data.frame(tax_table(ps2024_exp_co1)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_exp_co1) <- taxonomy_exp_co1$ASV
taxonomy_exp_co1 <- taxonomy_exp_co1 %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_exp_co1) <- as.matrix(taxonomy_exp_co1)


taxonomy_trawl_mifish <- as.data.frame(tax_table(ps2024_trawl_mifish)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_trawl_mifish) <- taxonomy_trawl_mifish$ASV
taxonomy_trawl_mifish <- taxonomy_trawl_mifish %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_trawl_mifish) <- as.matrix(taxonomy_trawl_mifish)

taxonomy_trawl_elas <- as.data.frame(tax_table(ps2024_trawl_elas)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_trawl_elas) <- taxonomy_trawl_elas$ASV
taxonomy_trawl_elas <- taxonomy_trawl_elas %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_trawl_elas) <- as.matrix(taxonomy_trawl_elas)

taxonomy_trawl_co1 <- as.data.frame(tax_table(ps2024_trawl_co1)) %>%
  rownames_to_column("ASV") %>%
  left_join(commonnames, by = c("Species" = "Taxon"))
row.names(taxonomy_trawl_co1) <- taxonomy_trawl_co1$ASV
taxonomy_trawl_co1 <- taxonomy_trawl_co1 %>% select(-ASV)
# Update the phyloseq object
tax_table(ps2024_trawl_co1) <- as.matrix(taxonomy_trawl_co1)

# Check
data.frame(tax_table(ps2024_exp_mifish))
data.frame(tax_table(ps2024_exp_elas))
data.frame(tax_table(ps2024_exp_co1))

data.frame(tax_table(ps2024_trawl_mifish))
data.frame(tax_table(ps2024_trawl_elas))
data.frame(tax_table(ps2024_trawl_co1))
```

#### Save variables up to here
```{r}
save.image(file = "figures-expedition/phyloseq_objects_filtered.RData")
```

load if returning
```{r}
load("figures-expedition/phyloseq_objects_filtered.RData")
```


### Controls
Check remaining ASVs in neg controls 

MiFish/ Expedition-
```{r}
data.frame(otu_table(ps2024_exp_mifish)[,which(sample_data(ps2024_exp_mifish)$controls == "negative")])
max(otu_table(ps2024_exp_mifish)[,which(sample_data(ps2024_exp_mifish)$controls == "negative")])
```



Elas02/ Expedition-
```{r}
data.frame(otu_table(ps2024_exp_elas)[,which(sample_data(ps2024_exp_elas)$controls == "negative")])
max(otu_table(ps2024_exp_elas)[,which(sample_data(ps2024_exp_elas)$controls == "negative")])
```



CO1/ Expedition-
```{r}
data.frame(otu_table(ps2024_exp_co1)[,which(sample_data(ps2024_exp_co1)$controls == "negative")])
max(otu_table(ps2024_exp_co1)[,which(sample_data(ps2024_exp_co1)$controls == "negative")])
```


```{r}
neg_controls_df <- data.frame(otu_table(ps2024_exp_co1)[, which(sample_data(ps2024_exp_co1)$controls == "negative")])
neg_controls_df$TotalAbundance <- rowSums(neg_controls_df)
neg_controls_sorted <- neg_controls_df %>%
  arrange(desc(TotalAbundance))

neg_controls_sorted


# what is the taxonomy of these
df.neg.ASVs <- as.data.frame(tax_table(phylo_2024_exp_co1)[rownames(data.frame(otu_table(ps2024_exp_co1)[,which(sample_data(ps2024_exp_co1)$controls == "positive")]))])

df.neg.ASVs[rownames(neg_controls_sorted),]
```



MiFish/ Trawl-
```{r}
data.frame(otu_table(ps2024_trawl_mifish)[,which(sample_data(ps2024_trawl_mifish)$controls == "negative")])
max(otu_table(ps2024_trawl_mifish)[,which(sample_data(ps2024_trawl_mifish)$controls == "negative")])
```

Elas/ Trawl-
```{r}
data.frame(otu_table(ps2024_trawl_elas)[,which(sample_data(ps2024_trawl_elas)$controls == "negative")])
max(otu_table(ps2024_trawl_elas)[,which(sample_data(ps2024_trawl_elas)$controls == "negative")])
```




CO1/ Trawl-
```{r}
data.frame(otu_table(ps2024_trawl_co1)[,which(sample_data(ps2024_trawl_co1)$controls == "negative")])
max(otu_table(ps2024_trawl_co1)[,which(sample_data(ps2024_trawl_co1)$controls == "negative")])
```
```{r}
neg_controls_df <- data.frame(otu_table(ps2024_trawl_co1)[, which(sample_data(ps2024_trawl_co1)$controls == "negative")])
neg_controls_df$TotalAbundance <- rowSums(neg_controls_df)
neg_controls_sorted <- neg_controls_df %>%
  arrange(desc(TotalAbundance))

neg_controls_sorted


# what is the taxonomy of these
df.neg.ASVs <- as.data.frame(tax_table(phylo_2024_trawl_co1)[rownames(data.frame(otu_table(ps2024_trawl_co1)[,which(sample_data(ps2024_trawl_co1)$controls == "positive")]))])

df.neg.ASVs[rownames(neg_controls_sorted),]
```

Check which species are abundant in the pos controls 


Exp/MiFish-
```{r}
df.pos <- as.data.frame(otu_table(ps2024_exp_mifish)[,which(sample_data(ps2024_exp_mifish)$controls == "positive")])

# arrange ASVs from pos ctl in descending order to see most abundant
df.pos <- df.pos %>% mutate(Sum = MP_C_4ES2_S25_L001+MP_C_5ES2_S25_L001) %>% arrange(desc(Sum))
df.pos
  
# what is the taxonomy of these
df.pos.ASVs <- as.data.frame(tax_table(phylo_2024_exp_mifish)[rownames(data.frame(otu_table(ps2024_exp_mifish)[,which(sample_data(ps2024_exp_mifish)$controls == "positive")]))])

df.pos.ASVs[rownames(df.pos),]
```



Remove ASVs with less than 500 reads in a sample. 

Exp/MiFish-
```{r}
data.frame(otu_table(ps2024_exp_mifish)) # compare before

ps2024_exp_mifish <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2024_exp_mifish,
  minabund = 500,
  relabund = FALSE)

data.frame(otu_table(ps2024_exp_mifish)) # and after
```





Exp/Elas02-
```{r}
data.frame(otu_table(ps2024_exp_elas)) # compare before

ps2024_exp_elas <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2024_exp_elas,
  minabund = 500,
  relabund = FALSE)

data.frame(otu_table(ps2024_exp_elas)) # and after
```


Exp/CO1-

```{r}
df.pos <- as.data.frame(otu_table(ps2024_exp_co1)[,which(sample_data(ps2024_exp_co1)$controls == "positive")])

# arrange ASVs from pos ctl in descending order to see most abundant
df.pos <- df.pos %>% mutate(Sum = MP_C_4_S1_L001+MP_C_5_S1_L001) %>% arrange(desc(Sum))
df.pos
  
# what is the taxonomy of these
df.pos.ASVs <- as.data.frame(tax_table(phylo_2024_exp_co1)[rownames(data.frame(otu_table(ps2024_exp_co1)[,which(sample_data(ps2024_exp_co1)$controls == "positive")]))])

df.pos.ASVs[rownames(df.pos),]
```


Trawl/MiFish-
```{r}
data.frame(otu_table(ps2024_trawl_mifish)) # compare before

ps2024_trawl_mifish <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2024_trawl_mifish,
  minabund = 500,
  relabund = FALSE)

data.frame(otu_table(ps2024_trawl_mifish)) # and after
```




Trawl/Elas02-
```{r}
data.frame(otu_table(ps2024_trawl_elas)) # compare before

ps2024_trawl_elas <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2024_trawl_elas,
  minabund = 500,
  relabund = FALSE)

data.frame(otu_table(ps2024_trawl_elas)) # and after
```




Trawl/CO1-

```{r}
df.pos <- as.data.frame(otu_table(ps2024_trawl_co1)[,which(sample_data(ps2024_trawl_co1)$controls == "positive")])

# arrange ASVs from pos ctl in descending order to see most abundant
df.pos <- df.pos %>% mutate(Sum = MP_S_Positive_S1_L001+MP_STPositive_S1_L001
) %>% arrange(desc(Sum))
df.pos
  
# what is the taxonomy of these
df.pos.ASVs <- as.data.frame(tax_table(phylo_2024_trawl_co1)[rownames(data.frame(otu_table(ps2024_trawl_co1)[,which(sample_data(ps2024_trawl_co1)$controls == "positive")]))])

df.pos.ASVs[rownames(df.pos),]
```




#### Save variables up to here 
```{r}
save.image(file = "figures-expedition/environment_upto_filtering_controls.RData")
```

load if returning
```{r}
load("figures-expedition/environment_upto_filtering_controls.RData")
```


### Agglomerate by taxonomy

Exp/MiFish-
```{r}
ps2024_exp_mifish_glommed <- tax_glom(ps2024_exp_mifish, "Taxon.CommonName")

# plot total reads
plot_bar(ps2024_exp_mifish_glommed, x = "Name.Deploy_Cartr_Library")

# view tax_table
data.frame(tax_table(ps2024_exp_mifish_glommed))
```



Exp/Elas02-
```{r}
ps2024_exp_elas_glommed <- tax_glom(ps2024_exp_elas, "Taxon.CommonName")

# plot total reads
plot_bar(ps2024_exp_elas_glommed, x = "Name_Deploy_Cartr_Library")

# view tax_table
data.frame(tax_table(ps2024_exp_elas_glommed))
```


Exp/CO1-


```{r}
ps2024_exp_co1_glommed <- tax_glom(ps2024_exp_co1, "Species")

# plot total reads
plot_bar(ps2024_exp_co1, x = "Name_Deploy_Cartr")

# view tax_table
data.frame(tax_table(ps2024_exp_co1_glommed))
```


Trawl/MiFish-
```{r}
ps2024_trawl_mifish_glommed <- tax_glom(ps2024_trawl_mifish, "Taxon.CommonName")

# plot total reads
plot_bar(ps2024_trawl_mifish_glommed)

# view tax_table
data.frame(tax_table(ps2024_trawl_mifish_glommed))
```

Trawl/MiFish-
```{r}
ps2024_trawl_elas_glommed <- tax_glom(ps2024_trawl_elas, "Taxon.CommonName")

# plot total reads
plot_bar(ps2024_trawl_elas_glommed)

# view tax_table
data.frame(tax_table(ps2024_trawl_elas_glommed))
```


Trawl/CO1-

```{r}
ps2024_trawl_co1_glommed <- tax_glom(ps2024_trawl_co1, "Species")

# plot total reads
plot_bar(ps2024_trawl_co1)

# view tax_table
data.frame(tax_table(ps2024_trawl_co1_glommed))
```

### Remove samples with low total number of reads. 

Exp/MiFish-
```{r}
ps2024_exp_mifish_glommed <- prune_samples(sample_sums(ps2024_exp_mifish_glommed)>=25000, ps2024_exp_mifish_glommed)
ps2024_exp_mifish <- prune_samples(sample_sums(ps2024_exp_mifish)>=25000, ps2024_exp_mifish)

# plot again
plot_bar(ps2024_exp_mifish_glommed, x = "Name.Deploy_Cartr_Library")

# how many samples remain?
dim(sample_data(ps2024_exp_mifish_glommed))[1]
dim(sample_data(ps2024_exp_mifish))[1]
```



Exp/ Elas02-
```{r}
ps2024_exp_elas_glommed <- prune_samples(sample_sums(ps2024_exp_elas_glommed)>=25000, ps2024_exp_elas_glommed)
ps2024_exp_elas <- prune_samples(sample_sums(ps2024_exp_elas)>=25000, ps2024_exp_elas)

# plot again
plot_bar(ps2024_exp_elas_glommed, x = "Name_Deploy_Cartr_Library")

# how many samples remain?
dim(sample_data(ps2024_exp_elas_glommed))[1]
dim(sample_data(ps2024_exp_elas))[1]
```



Exp/CO1-
```{r}
ps2024_exp_co1_glommed <- prune_samples(sample_sums(ps2024_exp_co1_glommed)>=25000, ps2024_exp_co1_glommed)
ps2024_exp_co1 <- prune_samples(sample_sums(ps2024_exp_co1)>=25000, ps2024_exp_co1)

# plot again
plot_bar(ps2024_exp_co1_glommed, x = "Name_Deploy_Cartr")

# how many samples remain?
dim(sample_data(ps2024_exp_co1_glommed))[1]
dim(sample_data(ps2024_exp_co1))[1]
```



Trawl/MiFish-
```{r}
ps2024_trawl_mifish_glommed <- prune_samples(sample_sums(ps2024_trawl_mifish_glommed)>=25000, ps2024_trawl_mifish_glommed)

ps2024_trawl_mifish <- prune_samples(sample_sums(ps2024_trawl_mifish)>=25000, ps2024_trawl_mifish)

# plot again
plot_bar(ps2024_trawl_mifish_glommed)

# how many samples remain?
dim(sample_data(ps2024_trawl_mifish_glommed))[1]
dim(sample_data(ps2024_trawl_mifish))[1]
```



Trawl/Elas-
```{r}
ps2024_trawl_elas_glommed <- prune_samples(sample_sums(ps2024_trawl_elas_glommed)>=25000, ps2024_trawl_elas_glommed)

ps2024_trawl_elas <- prune_samples(sample_sums(ps2024_trawl_elas)>=25000, ps2024_trawl_elas)

# plot again
plot_bar(ps2024_trawl_elas_glommed)

# how many samples remain?
dim(sample_data(ps2024_trawl_elas_glommed))[1]
dim(sample_data(ps2024_trawl_elas))[1]
```


Trawl/CO1-
```{r}
ps2024_trawl_co1_glommed <- prune_samples(sample_sums(ps2024_trawl_co1_glommed)>=25000, ps2024_trawl_co1_glommed)
ps2024_trawl_co1 <- prune_samples(sample_sums(ps2024_trawl_co1)>=25000, ps2024_trawl_co1)

# plot again
plot_bar(ps2024_trawl_co1_glommed)

# how many samples remain?
dim(sample_data(ps2024_trawl_co1_glommed))[1]
dim(sample_data(ps2024_trawl_co1))[1]
```



### Export Tables

Exp/MiFish-
```{r}
mifish_2024_exp_asv_table_taxbased <- data.frame(otu_table(ps2024_exp_mifish_glommed))
mifish_2024_exp_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_exp_mifish_glommed)), var = "1stRepresentative_ASV")
mifish_2024_exp_sample_data_taxbased <- data.frame(sample_data(ps2024_exp_mifish_glommed))


# view
mifish_2024_exp_asv_table_taxbased
mifish_2024_exp_tax_table_taxbased
mifish_2024_exp_sample_data_taxbased

# export
write.csv(mifish_2024_exp_asv_table_taxbased,"figures-expedition/mifish_2024_exp_asv_table_taxbased.csv", row.names = TRUE)
write.csv(mifish_2024_exp_tax_table_taxbased,"figures-expedition/mifish_2024_exp_tax_table_taxbased.csv", row.names = FALSE)
write.csv(mifish_2024_exp_sample_data_taxbased,"figures-expedition/mifish_2024_exp_sample_data_taxbased.csv", row.names = TRUE)
```


Exp/Elas02-
```{r}
elas_2024_exp_asv_table_taxbased <- data.frame(otu_table(ps2024_exp_elas_glommed))
elas_2024_exp_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_exp_elas_glommed)), var = "1stRepresentative_ASV")
elas_2024_exp_sample_data_taxbased <- data.frame(sample_data(ps2024_exp_elas_glommed))


# view
elas_2024_exp_asv_table_taxbased
elas_2024_exp_tax_table_taxbased
elas_2024_exp_sample_data_taxbased

# export
write.csv(elas_2024_exp_asv_table_taxbased,"figures-expedition/elas_2024_exp_asv_table_taxbased.csv", row.names = TRUE)
write.csv(elas_2024_exp_tax_table_taxbased,"figures-expedition/elas_2024_exp_tax_table_taxbased.csv", row.names = FALSE)
write.csv(elas_2024_exp_sample_data_taxbased,"figures-expedition/elas_2024_exp_sample_data_taxbased.csv", row.names = TRUE)
```


Exp/CO1-
```{r}
co1_2024_exp_asv_table_taxbased <- data.frame(otu_table(ps2024_exp_co1_glommed))
co1_2024_exp_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_exp_co1_glommed)), var = "1stRepresentative_ASV")
co1_2024_exp_sample_data_taxbased <- data.frame(sample_data(ps2024_exp_co1_glommed))

# agglomerating by Species deleted entries in columns following, so re-append common names so they are retained
co1_2024_exp_tax_table_taxbased <- co1_2024_exp_tax_table_taxbased %>%
  select(-CommonName, -Taxon.CommonName, -Color)

co1_2024_exp_tax_table_taxbased <- co1_2024_exp_tax_table_taxbased %>%
  left_join(commonnames, by = c("Species" = "Taxon"))

# view
co1_2024_exp_asv_table_taxbased
co1_2024_exp_tax_table_taxbased
co1_2024_exp_sample_data_taxbased

# export
write.csv(co1_2024_exp_asv_table_taxbased,"figures-expedition/co1_2024_exp_asv_table_taxbased.csv", row.names = TRUE)
write.csv(co1_2024_exp_tax_table_taxbased,"figures-expedition/co1_2024_exp_tax_table_taxbased.csv", row.names = FALSE)
write.csv(co1_2024_exp_sample_data_taxbased,"figures-expedition/co1_2024_exp_sample_data_taxbased.csv", row.names = TRUE)
```



Trawl/MiFish-
```{r}
mifish_2024_trawl_asv_table_taxbased <- data.frame(otu_table(ps2024_trawl_mifish_glommed))
mifish_2024_trawl_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_trawl_mifish_glommed)), var = "1stRepresentative_ASV")
mifish_2024_trawl_sample_data_taxbased <- data.frame(sample_data(ps2024_trawl_mifish_glommed))


# view
mifish_2024_trawl_asv_table_taxbased
mifish_2024_trawl_tax_table_taxbased
mifish_2024_trawl_sample_data_taxbased

# export
write.csv(mifish_2024_trawl_asv_table_taxbased,"figures-expedition/mifish_Sept2024_trawl_asv_table_taxbased.csv", row.names = TRUE)
write.csv(mifish_2024_trawl_tax_table_taxbased,"figures-expedition/mifish_Sept2024_trawl_tax_table_taxbased.csv", row.names = FALSE)
write.csv(mifish_2024_trawl_sample_data_taxbased,"figures-expedition/mifish_Sept2024_trawl_sample_data_taxbased.csv", row.names = TRUE)
```




Trawl/Elas-
```{r}
elas_2024_trawl_asv_table_taxbased <- data.frame(otu_table(ps2024_trawl_elas_glommed))
elas_2024_trawl_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_trawl_elas_glommed)), var = "1stRepresentative_ASV")
elas_2024_trawl_sample_data_taxbased <- data.frame(sample_data(ps2024_trawl_elas_glommed))


# view
elas_2024_trawl_asv_table_taxbased
elas_2024_trawl_tax_table_taxbased
elas_2024_trawl_sample_data_taxbased

# export
write.csv(elas_2024_trawl_asv_table_taxbased,"figures-expedition/elas_Sept2024_trawl_asv_table_taxbased.csv", row.names = TRUE)
write.csv(elas_2024_trawl_tax_table_taxbased,"figures-expedition/elas_Sept2024_trawl_tax_table_taxbased.csv", row.names = FALSE)
write.csv(elas_2024_trawl_sample_data_taxbased,"figures-expedition/elas_Sept2024_trawl_sample_data_taxbased.csv", row.names = TRUE)
```


Trawl/Co1-
```{r}
co1_2024_trawl_asv_table_taxbased <- data.frame(otu_table(ps2024_trawl_co1_glommed))
co1_2024_trawl_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2024_trawl_co1_glommed)), var = "1stRepresentative_ASV")
co1_2024_trawl_sample_data_taxbased <- data.frame(sample_data(ps2024_trawl_co1_glommed))


# view
co1_2024_trawl_asv_table_taxbased
co1_2024_trawl_tax_table_taxbased
co1_2024_trawl_sample_data_taxbased

# export
write.csv(co1_2024_trawl_asv_table_taxbased,"figures-expedition/co1_Sept2024_trawl_asv_table_taxbased.csv", row.names = TRUE)
write.csv(co1_2024_trawl_tax_table_taxbased,"figures-expedition/co1_Sept2024_trawl_tax_table_taxbased.csv", row.names = FALSE)
write.csv(co1_2024_trawl_sample_data_taxbased,"figures-expedition/co1_Sept2024_trawl_sample_data_taxbased.csv", row.names = TRUE)
```




Also calculate *relative abundances* (# of ASV sequences/sum total sequences in sample), for some plotting

```{r}
ps2024_exp_mifish_ra <- microbiome::transform(ps2024_exp_mifish, transform = "compositional")
ps2024_exp_mifish_glommed_ra <- microbiome::transform(ps2024_exp_mifish_glommed, transform = "compositional")

ps2024_exp_elas_ra <- microbiome::transform(ps2024_exp_elas, transform = "compositional")
ps2024_exp_elas_glommed_ra <- microbiome::transform(ps2024_exp_elas_glommed, transform = "compositional")

ps2024_exp_co1_ra <- microbiome::transform(ps2024_exp_co1, transform = "compositional")
ps2024_exp_co1_glommed_ra <- microbiome::transform(ps2024_exp_co1_glommed, transform = "compositional")



ps2024_trawl_mifish_ra <- microbiome::transform(ps2024_trawl_mifish, transform = "compositional")
ps2024_trawl_mifish_glommed_ra <- microbiome::transform(ps2024_trawl_mifish_glommed, transform = "compositional")

ps2024_trawl_elas_ra <- microbiome::transform(ps2024_trawl_elas, transform = "compositional")
ps2024_trawl_elas_glommed_ra <- microbiome::transform(ps2024_trawl_elas_glommed, transform = "compositional")

ps2024_trawl_co1_ra <- microbiome::transform(ps2024_trawl_co1, transform = "compositional")
ps2024_trawl_co1_glommed_ra <- microbiome::transform(ps2024_trawl_co1_glommed, transform = "compositional")

```


Export relative abundance tables
```{r}
mifish_2024_exp_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_exp_mifish_glommed_ra))
elas_2024_exp_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_exp_elas_glommed_ra))
co1_2024_exp_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_exp_co1_glommed_ra))

mifish_2024_trawl_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_trawl_mifish_glommed_ra))
elas_2024_trawl_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_trawl_elas_ra))
co1_2024_trawl_asv_table_taxbased_RA <- data.frame(otu_table(ps2024_trawl_co1_ra))


# view
mifish_2024_exp_asv_table_taxbased_RA
elas_2024_exp_asv_table_taxbased_RA
co1_2024_exp_asv_table_taxbased_RA
mifish_2024_trawl_asv_table_taxbased_RA
elas_2024_trawl_asv_table_taxbased_RA
co1_2024_trawl_asv_table_taxbased_RA


# export
write.csv(mifish_2024_exp_asv_table_taxbased_RA,"figures-expedition/mifish_2024_exp_asv_table_taxbased_RA.csv", row.names = TRUE)
write.csv(elas_2024_exp_asv_table_taxbased_RA,"figures-expedition/elas_2024_exp_asv_table_taxbased_RA.csv", row.names = TRUE)
write.csv(co1_2024_exp_asv_table_taxbased_RA,"figures-expedition/co1_2024_exp_asv_table_taxbased_RA.csv", row.names = TRUE)

write.csv(mifish_2024_trawl_asv_table_taxbased_RA,"figures-expedition/mifish_2024_trawl_asv_table_taxbased_RA.csv", row.names = TRUE)
write.csv(elas_2024_trawl_asv_table_taxbased_RA,"figures-expedition/elas_2024_trawl_asv_table_taxbased_RA.csv", row.names = TRUE)
write.csv(co1_2024_trawl_asv_table_taxbased_RA,"figures-expedition/co1_2024_trawl_asv_table_taxbased_RA.csv", row.names = TRUE)


```


#### Save
```{r}
save.image(file = "figures-expedition/environment_upto_export.RData")
```

load if returning
```{r}
load("figures-expedition/figures-expedition/environment_upto_export.RData")
```



